Robust Co-occurrence Quantification for Lexical Distributional Semantics

### 2016-05-31 paper.tex
Intro

>>>>

Words that occur in similar context have similar meaning \cite{harris1954distributional}. Thus the meaning of a word can be modeled by counting its co-occurrence with neighboring words in a corpus. Distributional models of meaning represent co-occurrence information in a vector space, where the dimensions are the neighboring words and the values are co-occurrence counts. Successful models need to be able to discriminate co-occurrence information, as not all co-occurrence counts are equally useful, for instance, the co-occurrence with the article \textit{the} is less informative than with a word \textit{existence}. Another fundamental question is the vector space dimensionality and what neighbor words correspond to them.
